%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Scientific Contributions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
    {}
    {Peer Reviewed Research}
    {}
    {}
    {}
    {
     \begin{cvitems}% Description(s)
     \vspace{-.8cm}
     \descriptionstyle{
      \item{Zhao, Z., \textbf{\underline{Woloszynek, S.}}, Agbavor, F., Mell, J. C., Sokhansanj, B. A., and Rosen, G. L. Learning, Visualizing and Exploring 16S rRNA Structure Using an Attention-Based Deep Neural Network. Submitted for Publication}
        \item{Price, J.R., \textbf{\underline{Woloszynek, S.}}, Rosen, G.L., and C.M. Sales. Quantifying the influence of nutrient loading and availability on microbial community dynamics and subsequent kinetic behavior. In Review.}
        \item{Smith, S. H., O'Connor, M. P., Deal, B., Kotzer, C., Lee, A. Wagner, B., Joffe, J., Peng, L., Carpenter, M., \textbf{\underline{Woloszynek, S.}}, Oliver, K. M., Russell, J. A. Does getting defensive get you anywhere?— Seasonal balancing selection in pea aphids shapes a dynamic infection polymorphism with a protective bacterial endosymbiont. In Review.}
        \item{\href{https://doi.org/10.1371/journal.pone.0219235}{\textbf{\underline{Woloszynek, S.}}, Mell, J. C., Zhao, Z., Simpson, G., O’Connor, M. P., and Rosen, G. Exploring thematic structure and predicted functionality of 16S rRNA amplicon data. 2019. PLoS ONE 14 (12).}}
        \item{\href{https://doi.org/10.1371/journal.pcbi.1006721}{\textbf{\underline{Woloszynek, S.}}, Zhao, Z., Chen, J., and Rosen, G. 16S rRNA sequence embeddings: Meaningful numeric feature representations of nucleotide sequences that are convenient for downstream analyses. 2019. PLoS Comp Bio 15 (2).}}
        \item{\href{https://doi.org/10.1186/s40168-017-0339-6}{O’Hara, N. B., Reed, H. J., Afshinnekoo, E., Harvin, D., Caplan, N., Rosen, G., Frye, B., \textbf{\underline{Woloszynek, S.}}, Ounit, R., Levy, S., Butler, E., and Mason, C. E. Metagenomic characterization of ambulances across the USA. 2017. Microbiome 5 (1).}}
        \item{\href{https://doi.org/10.1371/journal.pone.0134464}{Cronin, D., \textbf{\underline{Woloszynek, S.}}, Morra, W. A., Honarvar, S., Linder, J. M., Gonder, M. K., O’Conner, M. P., and Hearn, G. W. Long–term urban market dynamics reveal increased bushmeat carcass volume despite economic growth and proactive environmental legislation on Bioko Island, Equatorial Guinea. 2015. PLoS ONE 10 (7).}}
        \item{\href{https://doi.org/10.1007/s00467-011-2056-x}{Kangovi, S., Edwards, M., \textbf{\underline{Woloszynek, S.}}, Mitra, N., Feldman, H., Kaplan, B. S., and Meyers, K. E. Renin–angiotensin–aldosterone system inhibitors in pediatric focal segmental glomerulosclerosis. 2012. Pediatric Nephrology. 27 (5): 813–9.}}
        }
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}
    {Chapters and Reviews}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{\href{https://doi.org/10.3389/fmicb.2020.00136}{Cullen, C., Aneja, K. K., Beyhan, S., Cho, C. E., \textbf{\underline{Woloszynek, S.}}, Convertino, M., Mccoy, S. J., Zhang, Y., Anderson, M., Alvarez-Ponce, D., Smirnova, E., Karstens, L., Dorrenstein, P. C., Li, H., Gupta, A. S., Cheung, K., Powers, J. G., Zhao, Z., and Rosen, G. Emerging Priorities for Microbiome Research. 2020. Frontiers in Microbiology.}}
        \item{\href{https://doi.org/10.1007/978-3-319-74974-7}{\textbf{\underline{Woloszynek, S.}}, Zhao, Z., Ditzler, G., Price, J. R., Reichenberger, E. R., Lan, Y., Chen, J., Earl, J., Langroodi, S. K., Ehrlich, G., and Rosen, G. Analysis Methods for Shotgun Metagenomics. 2018. Theoretical and Applied Aspects of Systems Biology. Springer.}}
        \item{\href{https://doi.org/10.1098/rsif.2017.0387}{Ching, T., Himmelstein, D. S., Beaulieu-Jones, B. K., Kalinin, A.A., Do, B. T., Way, G.P., Ferrero, E., Agapow, P.M., Zietz, M., Hoffman, M.M., Xie, W., Rosen, G. L., Lengerich, B.J., Israeli, J., Lanchantin, J., \textbf{\underline{Woloszynek, S.}}, Carpenter, A. E., Shrikumar, A., Xu, J., Cofer, E. M., Lavender, C. A. Turaga, S. C., Alexandari, A. M., Lu, Z., Harris, D. J., DeCaprio, D., Qi, Y., Kundaje, A., Peng, Y., Wiley, L. K., Segler, M. H. S., Boca, S. M., Swamidass, S. J., Huang, A., Gitter, A., and Greene C. S. Opportunities and obstacles for deep learning in biology and medicine. 2018. Journal of the Royal Society Interface. 15 (141).}}
        \item{\href{https://doi.org/10.1016/bs.ircmb.2016.01.003}{\textbf{\underline{Woloszynek, S.}}, Pastor, S. J., Mell, J. C., Nandi, N., Sokhansanj, B., and Rosen, G. Engineering human microbiota: influencing cellular and community dynamics for therapeutic applications. 2016. IRCMB. 324: 67-124.}}
        }
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}
    {Conference Papers and Abstracts}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{Venditti, D., \textbf{\underline{Woloszynek, S.}}, Zhao, Z., Rosen, Morra, W., Ondo nze avomo, J., G. L., Cronin, D., O’Conner, M. P., Hearn, G. W., and Gonder. Understanding an unsustainable Central African bushmeat commodity chain: A multidisciplinary approach. 2020. IPS.}
        \item{Venditti, D., \textbf{\underline{Woloszynek, S.}}, Zhao, Z., Rosen, Morra, W., Ondo nze avomo, J., G. L., Cronin, D., O’Conner, M. P., Hearn, G. W., and Gonder. Understanding an unsustainable Central African bushmeat commodity chain: A multidisciplinary approach. 2020. STE.}
        \item{Smith, A. H., O’Connor, M. P., \textbf{\underline{Woloszynek, S.}}, Oliver, K. M., and Russell, J. A. Does getting defensive get you anywhere? - Dissecting the causes of rapid symbiont dynamics in the pea aphid. 2018. Wolbachia meetings.}
        \item{Price, J., Nan, Y., Wang, Y., Cheng, M., Keshani, S., \textbf{\underline{Woloszynek, S.}}, Rosen, G., Yuan, L., and Sales, C. Predation and parasitism induces community stability and performance within EBPR reactors. 2019. American chemical society 257.}
        \item{Mitchell, M. W., \textbf{\underline{Woloszynek, S.}}, Al-Ghalith, G., Clayton, J. B., Rosen, G. L., Gonder, M. K., and Knights, D. Habitat variation impacts chimpanzee gut microbiome diversity in Cameroon. 2018. International Society of Primatologists, Nairobi.}
        \item{Vanderkluysen, L., Barber, N., \textbf{\underline{Woloszynek, S.}}, O’Connor, M. P., Mittal, T., Sealing, C., Sprain, C., and Renne, P. Statistical Analysis of Deccan Basalt Geochemistry: An Updated Look at Deccan Chemostratigraphy. 2017. American Geophysical Union.}
        \item{Vanderkluysen, L., Barber, N., \textbf{\underline{Woloszynek, S.}}, O’Connor, M. P., Mittal, T., Sealing, C., Sprain, C., and Renne, P. A Modern Look at the Deccan Chemostratigraphic Scheme. 2017. Geological Society of America.}
         \item{Cronin, D. T., \textbf{\underline{Woloszynek, S.}}, Long term monitoring of a bushmeat market in Bioko, Equatorial Guinea. 2014. Annual Meeting of the Society for Integrative and Comparative Biology.}
         }
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}
    {Working Papers}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{O’Hara, N. B., Reed, H. J., Afshinnekoo, E., Harvin, D., Caplan, N., Rosen, G., Frye, B., \textbf{\underline{Woloszynek, S.}}, Ounit, R., Levy, S., Butler, E., and Mason, C. E. Further Metagenomic characterization of ambulances across the USA.}
        \item{Venditti, D., \textbf{\underline{Woloszynek, S.}}, Zhao, Z., Rosen, G. L., Cronin, D., O’Conner, M. P., Hearn, G. W., and Gonder, M. K. Long–term urban bushmeat market dynamics on Bioko Island, Equatorial Guinea. }
        \item{Owens, J. R., \textbf{\underline{Woloszynek, S.}}, Lei, B. W., Hou, R., Qi, D., Kilham, B., Spotila, J. R., Yi, S., Spotila, J. T., and Zhang, Z. Reintroduction conditioning and the influence of human interactions and care on the behavior of giant pandas.}
        \item{Nan, Y., Price, J. R., Keshani, S., \textbf{\underline{Woloszynek, S.}}, Rosen, G. L., and Sales, C. M. Evidence of predation and parasitism affecting EBPR performance through microbial community instability. }
        \item{Mitchell, M. W., \textbf{\underline{Woloszynek, S.}}, Al-Ghalith, Featherstone, B. S., G., Clayton, J. B., Rosen, G. L., Gonder, M. K., and Knights, D. Environmental drivers shape the chimpanzee gut microbiome in a biodiversity hotspot.}
        }
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}
    {Invited Talks}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{\textbf{\underline{Woloszynek, S.}}, Mell, J. C., Simpson, G., and Rosen, G. Identifying microbial subcommunities associated with host metadata via a topic modelling framework. 214th Meeting of the Interurban Clinical Club. November 4, 2016. University of Pennsylvania. Philadelphia, PA.}
        \item{\textbf{\underline{Woloszynek, S.}}, Mell, J. C., Simpson, G., and Rosen, G. Identifying microbial subcommunities associated with host metadata via a topic modelling framework. International Symposium on Molecular Medicine and Infectious Disease. September 15, 2016. Drexel University College of Medicine. Philadelphia, PA.}
        }
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}
    {Poster Presentations}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{\textbf{\underline{Woloszynek, S.}}, Zhao, Z., O’Connor, M., Mell, J. C., Simpson, G., and Rosen G. Themetagenomics: Uncovering thematic structure in 16S rRNA marker gene survey. (1) Discovery Day. Drexel University, Philadelphia, PA, 2018. (2) Emerging Graduate Scholars Conference. Drexel University, Philadelphia, PA, 2018. (3) DIG’s 10th Annual Research Symposium, Drexel University, Philadelphia, PA, 2018, \textbf{2nd place}. (4) Microbiome, Host Resistance and Disease X4. Banff, Alberta, Canada, 2018.}
        \item{\textbf{\underline{Woloszynek, S.}}, Mell, J. C., Simpson, G., and Rosen, G. Identifying Microbial Subcommunities Associated with Host Metadata via a Topic Modelling Framework. (1) Penn PROMOTES Retreat, University of Pennsylvania, Philadelphia, PA, 2017. (2) DIG’s 9th Annual Research Symposium, Drexel University, Philadelphia, PA, 2017, (3) IHMC 2016. Houston, TX, 2016. (4) 3rd Annual Microbiome Symposium. Children’s Hospital of Philadelphia. Philadelphia, PA, 2016. (5) 2016 Mid Atlantic Bioinformatics Conference. Children’s Hospital of Philadelphia. Philadelphia, PA, 2016. (6) Discovery Day 2016, Drexel University College of Medicine, Philadelphia, PA, 2016.}
        \item{\textbf{\underline{Woloszynek, S.}}, Mell, J. C., and Rosen, G. Uncovering Metagenomic Topics Associated with Host Metadata. (1) Bridging Biomedical Worlds 2016. Hong Kong, China, 2016.}
        \item{\textbf{\underline{Woloszynek, S.}}, Tabb, L. P., and Rosen, G. Accounting for Zero-Inflation and Taxon-Correlations in Human Microbiome Data. DIG’s 8th Annual Research Symposium, Drexel University, Philadelphia, PA, 2016.}
        \item{\textbf{\underline{Woloszynek, S.}}, Tabb, L. P., and Rosen, G. A Zero–Inflated MVPLN Model for Correlated OTU Abundances. Discovery Day 2015, Drexel University College of Medicine, Philadelphia, PA, 2015.}
        \item{\textbf{\underline{Woloszynek, S.}}, Tabb, L. P., and Rosen, G. Overcoming Zero Inflation in Sparse OTU Tables. DTRA/NSF Workshop: Algorithms for Threat Detection, NSF, Arlington, VA, 2015.}
        \item{\textbf{\underline{Woloszynek, S.}}, Rosen, G. Prediction of Host Traits through Microbiota Composition via Supervised LDA. Research Day 2015, Drexel University, Philadelphia, PA, 2015.}
        \item{\textbf{\underline{Woloszynek, S.}}, Sperling, M., Sharan, A., and Jacobs, J. Electrocorticographic Recordings Reveal Distinct Neural Patterns for Working Memory Performance. (1) NE Regional APSA Meeting, Temple University, Philadelphia, PA, 2013. (2) Discovery Day 2013, Drexel University College of Medicine, Philadelphia, PA, 2013.}
        \item{Cronin, D.T., \textbf{\underline{Woloszynek, S.}}, Morra, W.A., Honarvar, S., Linder, J.M., O’Connor, M.P., Hearn, G.W. Emergent trends in an urban bushmeat market on Bioko Island, Equatorial Guinea. XXIV. Congress of the International Primatological Society, Cancun, Mexico, 2012.}
        \item{Cronin, D.T., \textbf{\underline{Woloszynek, S.}}, O’Connor, M.P., Hearn, G.W. Bushmeat Hunting on Bioko Island, Equatorial Guinea Suggests a Network of Organized Crime. 14th Annual Research Day, Drexel University, Philadelphia, PA, 2012.}
        \item{Cronin, D.T., \textbf{\underline{Woloszynek, S.}}, O’Connor, M.P., Hearn, G.W. Bushmeat Hunting on Bioko Island, Equatorial Guinea Suggests a Network of Organized Crime. 6th College of Arts and Sciences. Research Day, Drexel University, Philadelphia, PA, 2012.}
        \item{Kangovi, S., Edwards, M., \textbf{\underline{Woloszynek, S.}}, Feldman, H., Kaplan, B. S., and Meyers, K. RAAS Inhibitor Monotherapy in Pediatric FSGS Patients. Pediatric Academic Societies' and Asian Society for Pediatric Research Joint Meeting, Denver, CO, 2011.}
        \item{Cronin, D. T., \textbf{\underline{Woloszynek, S.}}, Morra, W., Biacho, R. A., and Hearn, G. Changing composition of the Malabo bushmeat market, Bioko Island, Equatorial Guinea, XXIII Congress of the International Primatological Society, Kyoto, Japan, 2010.}
        }
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}
    {Software and Packages}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{\href{https://cran.r-project.org/package=themetagenomics}{Themetagenomics. \textbf{\underline{Woloszynek, S.}}, R package version 1.0.2.}, \href{https://github.com/sw1/themetagenomics}{github.com/sw1/themetagenomics}}
        \item{\href{https://cran.r-project.org/package=theseus}{Theseus. Price, J. R. and \textbf{\underline{Woloszynek, S.}}, R package version 0.1.0.}, \href{https://github.com/sw1/theseus/}{github.com/sw1/theseus}}
	\item{\href{https://doi.org/10.1101/140855}{Biomod2EZ. Sesnek Clee, P. R., \textbf{\underline{Woloszynek, S.}}, and Gonder, M. K. 2017.}, \href{https://github.com/spsesinkclee/biomod2ez/}{\href{https://doi.org/10.1101/140855}{doi.org/10.1101/140855}, \href{https://github.com/psesinkclee/biomod2ez}{github.com/psesinkclee/biomod2ez}}}
	}
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}
    {Media Coverage}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{\href{https://www.npr.org/sections/goatsandsoda/2015/08/14/431965684/laws-to-prohibit-bush-meat-are-actually-a-boon-for-the-bush-meat-biz}{``Laws Prohibiting Bush Meat Are Actually A Boon For The Bush Meat Biz.'' NPR. August 2015.}}
        \item{\href{https://www.iflscience.com/plants-and-animals/hunting-primates-increases-economic-growth/}{``Hunting Of Primates Increases With Economic Growth.'' IFLScience. August 2015.}}
        }
      \end{cvitems}
    }
    
\vspace{1cm}
\cventry
    {}  
    {Peer Reviewer}
    {}
    {}
    {}
    {
     \begin{cvitems} % Description(s)
          \vspace{-.8cm}
     \descriptionstyle{
        \item{mSystems, Editor: Gail L. Rosen PhD}
        \item{Frontiers in Microbiology, Editor: Michele Guindani PhD}
        \item{PeerJ, Editor: Ka-Chun Wong PhD}
        }
      \end{cvitems}
    }
\end{cventries}

\vspace{.7cm}